\textbf{\sc Towards Deliberative Control of Autonomous Robots}

### 2012-02-16 trunk/europa-basics.tex
updates to europa text, figs and citations

\subsection{The basics}
\label{sec:basics}

@@

@@

For such a robot the milk buying plan at the store might look like
\comment{Figure needed}.

>>>>

\paragraph {A brief note on \texttt{EUROPA} history and notation} A
brief word about the history of planning paradigm and its
implementation in this chapter. The earliest origin of what we will
call \eu is from the \texttt{HSTS} planner \cite{mus94} which was used
for a number of demonstrations for space telescopes as noted in
Section \ref{sec:rabeyond}. \texttt{HSTS} was the
\texttt{LISP}-based\footnote{This was the first (and only to our
  knowledge) software ever to been written in \texttt{LISP} to be
  flown in space.} planner that was flown as part of the Remote Agent
\texttt{RAX} experiment. Concurrent to \texttt{RAX}, a C++ version of
the planner was designed at NASA Ames which went on to be used for the
\texttt{MAPGEN} system \cite{bresina05}. A vastly re-factored, higher
performance open source version \cite{europapso} was named \eu and is
the subject of this chapter. Note however, in using the name \eu, we
refer to the \emph{fundamental ideas as well as the planning paradigm}
even if there is a specific implementation online.

\subsection{The Basics}
\label{sec:basics}

@@

\begin{figure} \centering
  \includegraphics[scale=0.35]{figs/shopping_europa.pdf}
  \caption{\small A potential plan for a robot shopping for groceries.}
\label{fig:shop:shopping}
\vskip+0.1cm
\end{figure}

@@

For such a robot the milk buying plan at the store might look like
that shown in Fig. \ref{fig:shop:shopping}.
